Manuscript progress report

### 2023-12-06 Docs/manuscript.Rmd
small scale simulation

fig_adglmm_subset <- df_subset_adglmm %>% filter(id %in% rand_id2) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "GLMMadaptive", col = "Maximum observation time")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))

@@

```{r}
ggarrange(fig_fgfpca_subset, fig_adglmm_subset,
          nrow = 1, common.legend = T)
```

@@

```{r ise_GLMMadaptive_subset}
ise_mat_subset2 <- df_subset_adglmm %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err"))
colnames(ise_mat_subset2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r}
data.frame(Window = c("(0.2,0.4]", "(0.4,0.6]", "(0.6,0.8]", "(0.8, 1.0]"),
           ise_mat_subset, ise_mat_subset2, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

@@

```{r auc_GLMMadaptive_subset}
auc_mat_subset2 <- df_subset_adglmm %>%
  mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred0.2),
            auc2 = get_auc(Y, pred0.4),
            auc3 = get_auc(Y, pred0.6),
            auc4 = get_auc(Y, pred0.8)) %>%
  filter(window != "[0,0.2]") %>% 
  select(starts_with("auc"))

colnames(auc_mat_subset2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r}
data.frame(Window = c("(0.2,0.4]", "(0.4,0.6]", "(0.6,0.8]", "(0.8, 1.0]"),
           auc_mat_subset, auc_mat_subset2, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

@@

>>>>

fig_adglmm_subset <- pred_subset_adglmm[[1]] %>% 
  filter(id %in% rand_id2) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "GLMMadaptive", col = "Maximum observation time")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))

@@

```{r fit_sim_small, fig.height=4, fig.width=8}
ggarrange(fig_fgfpca_subset, fig_adglmm_subset,
          nrow = 1, common.legend = T)
```

@@

```{r ise_GLMMadaptive_subset}
for(m in 1:M2){
  this_df <- pred_subset_adglmm[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_mat_subset_ref[,,m] <- ise_tb_m
}

ise_mat_subset_ref <- apply(ise_mat_subset_ref, c(1, 2), mean)

colnames(ise_mat_subset_ref) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r}
data.frame(Window = c("(0.2,0.4]", "(0.4,0.6]", "(0.6,0.8]", "(0.8, 1.0]"),
           ise_mat_subset, ise_mat_subset_ref, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error", booktabs = T) %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

@@

```{r auc_GLMMadaptive_subset}
for(m in 1:M2){
  this_df <- pred_subset_adglmm[[m]]

  auc_mat_subset_ref[, , m] <- auc_tb_m

auc_mat_subset_ref <- apply(auc_mat_subset_ref, c(1,2), mean)
colnames(auc_mat_subset_ref) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r}
data.frame(Window = c("(0.2,0.4]", "(0.4,0.6]", "(0.6,0.8]", "(0.8, 1.0]"),
           auc_mat_subset, auc_mat_subset_ref, check.names = F) %>%
  kable(digits = 3, caption = "Area under the ROC curve", booktabs = T) %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

@@

```{r}
data.frame(
  "Method" = c("fGFPCA", "GLMMadaptive"),
  "Fit" = c(mean(fit_time_subset_fGFPCA)/60, mean(fit_time_subset_adglmm)),
           "Prediction"= c(mean(pred_time_subset_fGFPCA), mean(pred_time_subset_adglmm)/60)) %>%
  kable(digits = 3, caption = "Computation time (minutes)", booktabs = T) %>%
  kable_styling(full_width = F) 
```

### 2023-12-06 Docs/manuscript.tex
small scale simulation

\title{Manuscript progress report}
\author{Ying Jin}
\date{2023-12-05}

@@

\hypertarget{small-scale-simulation-one-iteration}{%
\section{Small-scale simulation: one
iteration}\label{small-scale-simulation-one-iteration}}

@@

I have used 100 subjects for training and testing. When fitting
GLMMadpative, I reduce the number of measurements to 1/10 by taking one
every 10 observations. The prediction is on the original grid.

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}

@@

\caption{\label{tab:unnamed-chunk-8}Integrated squared error}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{8}{c}{Observation track} \\
\cline{2-9}
\multicolumn{1}{c|}{ } & \multicolumn{4}{c|}{fGFPCA} & \multicolumn{4}{c}{GLMMadaptive} \\
\cline{2-5} \cline{6-9}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\hline
(0.2,0.4] & 154.178 &  &  &  & 387.140 &  &  & \\
\hline
(0.4,0.6] & 168.881 & 70.248 &  &  & 248.395 & 415.355 &  & \\
\hline
(0.6,0.8] & 235.562 & 47.770 & 16.813 &  & 330.585 & 321.804 & 265.975 & \\
\hline
(0.8, 1.0] & 97.413 & 77.682 & 19.947 & 12.015 & 186.022 & 525.561 & 349.314 & 116.319\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-9}Integrated squared error}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{8}{c}{Observation track} \\
\cline{2-9}
\multicolumn{1}{c|}{ } & \multicolumn{4}{c|}{fGFPCA} & \multicolumn{4}{c}{GLMMadaptive} \\
\cline{2-5} \cline{6-9}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\hline
(0.2,0.4] & 0.721 &  &  &  & 0.646 &  &  & \\
\hline
(0.4,0.6] & 0.658 & 0.725 &  &  & 0.620 & 0.665 &  & \\
\hline
(0.6,0.8] & 0.710 & 0.793 & 0.805 &  & 0.682 & 0.700 & 0.733 & \\
\hline
(0.8, 1.0] & 0.712 & 0.725 & 0.761 & 0.764 & 0.647 & 0.582 & 0.657 & 0.725\\
\hline
\end{tabular}
\end{table}

@@

@@

\caption{\label{tab:unnamed-chunk-10}Area Under the ROC curve}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Maximum observation time} \\
\cmidrule(l{3pt}r{3pt}){2-5}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{fGFPCA} & \multicolumn{2}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Window & 8am & 4pm & 8am & 4pm\\
\midrule
8am-4pm & 0.587 &  & 0.628 & \\
4am-midnight & 0.680 & 0.766 & 0.448 & 0.613\\
\bottomrule
\end{tabular}
\end{table}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}

>>>>

\title{Manuscript progress report}
\author{Ying Jin}
\date{2023-12-06}

@@

\hypertarget{small-scale-simulation}{%
\section{Small-scale simulation}\label{small-scale-simulation}}

@@

I have used 100 subjects for training and testing, and repeated 100
times. When fitting GLMMadpative, I reduce the number of measurements to
1/10 by taking one every 10 observations. The prediction is on the
original grid.

@@

\includegraphics{manuscript_files/figure-latex/fit_sim_small-1.pdf}

@@

\caption{\label{tab:unnamed-chunk-8}Integrated squared error}
\centering
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{8}{c}{Observation track} \\
\cmidrule(l{3pt}r{3pt}){2-9}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{fGFPCA} & \multicolumn{4}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\midrule
(0.2,0.4] & 151.709 &  &  &  & 374.368 &  &  & \\
(0.4,0.6] & 189.147 & 77.904 &  &  & 268.805 & 464.796 &  & \\
(0.6,0.8] & 226.314 & 51.773 & 17.050 &  & 321.530 & 286.806 & 230.564 & \\
(0.8, 1.0] & 113.007 & 81.718 & 19.576 & 13.244 & 227.965 & 472.162 & 341.146 & 136.831\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-10}Area under the ROC curve}
\centering
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{8}{c}{Observation track} \\
\cmidrule(l{3pt}r{3pt}){2-9}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{fGFPCA} & \multicolumn{4}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\midrule
(0.2,0.4] & 0.745 &  &  &  & 0.674 &  &  & \\
(0.4,0.6] & 0.663 & 0.733 &  &  & 0.623 & 0.671 &  & \\
(0.6,0.8] & 0.712 & 0.789 & 0.802 &  & 0.691 & 0.700 & 0.732 & \\
(0.8, 1.0] & 0.741 & 0.755 & 0.782 & 0.785 & 0.680 & 0.627 & 0.679 & 0.743\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-11}Computation time (minutes)}
\centering
\begin{tabular}[t]{lrr}
\toprule
Method & Fit & Prediction\\
\midrule
fGFPCA & 0.043 & 1.405\\
GLMMadaptive & 5.842 & 0.023\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-12}Area Under the ROC curve}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Maximum observation time} \\
\cmidrule(l{3pt}r{3pt}){2-5}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{fGFPCA} & \multicolumn{2}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Window & 8am & 4pm & 8am & 4pm\\
\midrule
8am-4pm & 0.587 &  & 0.628 & \\
4am-midnight & 0.680 & 0.766 & 0.448 & 0.613\\
\bottomrule
\end{tabular}
\end{table}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
